Understanding models for spatial structure in small-area estimation

### 2022-08-03 src/docs_paper/paper.Rmd
Some paper editing

---
title: Understanding models for spatial structure in small-area estimation
author:
  - name: Adam Howes
    email: ath19@ic.ac.uk
    affiliation: A
    corresponding: ath19@ic.ac.uk
  - name: Harrison Zhu
    affiliation: A
  - name: Yidan Xu
    affiliation: C
  - name: Samir Bhatt
    affiliation: D
  - name: Jeffrey W. Eaton
    affiliation: B
  - name: Seth R. Flaxman
    affiliation: E
address:
  - code: A
    address: Department of Mathematics, Imperial College London
  - code: B
    address: MRC Centre for Global Infectious Disease Analysis, Imperial College London
  - code: C
    address: Department of Statistics, University of Michigan
  - code: D
    address: Department of Public Health, University of Copenhagen
  - code: E
    address: Department of Computer Science, University of Oxford
abstract: |
  |  **Background:** Spatial correlation between small-areas is typically accounted for within a generalised linear mixed model setting using spatial random effects. However, commonly used models for spatial random effects based upon adjacency relations, like the Besag model, make unrealistic and unsatisfying spatial assumptions, which seem particularly dubious for irregular geometries. Furthermore, they do not take into account that across many settings areal data is generated by aggregating continuous point data. Defining spatial random effects which instead correspond to aggregated Gaussian processes gives a more intuitively convincing correlation structure, and allows tools from kernel methods to be used in models for areal data.
  |
  |  **Methods:** In a comprehensive simulation study, we used a proper scoring rule to evaluate the performance of different spatial random effect specifications. We performed these simulations under model misspecification and across a range of vignette and realistic geometries with different regularities. Finally, we compared model performance in estimating district-level HIV prevalence from PHIA household survey data across four countries in sub-Saharan Africa, using cross-validation and spatial cross-validation.
  |
  |  **Results:**
  |
  |  **Conclusions:**

@@

Spatial random effects are frequently used to model spatial variation in areal data [@haining2003spatial; @cramb2018investigation].
Gaussian Markov random fields (GMRFs) [@rue2005gaussian], which combine a Gaussian distribution with Markov conditional independence assumptions between areas, are the most common class of models used to specify spatial random effects.
Using a GMRF typically reflects the assumption that observations made in areas close together are correlated, and more distant relationships may be ignored.
The simplest GMRF model is arguably that of @besag1991bayesian, where information is borrowed equally from each adjacent area.
This model requires minimal additional modelling choices and is widely implemented, including as a part of the `R-INLA` package [@rue2017bayesian], popular within spatial statistics.
Use of this model is widespread, including in agriculture [@oliver2015soil], ecology [@saracco2010modeling], epidemiology [@lawson2013statistical], image analysis [@schmid2006bayesian], neuroscience [@gossl2001bayesian] and public health [@dwyer2015drinking].
However, for irregular geometries like the administrative divisions of a country, the assumptions made by the Besag model about space are unrealistic.
We hypothesised that incorporating a spatial structure more faithfully to the specific geometry would improve the performance of small-area estimation models.
Here, we set out to test this hypothesis, and in doing so provide practical recommendations for modelling spatial structure.
<!-- @gutreuter2019improving use the SAR model, which is still adjacency based but is not exactly the Besag model--restructure introduction to be more general and include introduction of other adjacency based models (which all have the same criticisms)? -->

@@

<!-- Within the GRMF framework, attempts to more accurately reflect irregular spatial structure have defined weights specifying the extent to which neighbours are related. -->
<!-- @duncan2017spatial compared seventeen methods for specifying these weights, but surprisingly did not find any which outperform the Besag model^[This conclusion was specific to the (often-analysed) Scottish lip cancer example, and like the majority of the literature, based on the deviance information criteria (DIC). The DIC is based on summarising the posterior distribution by a point estimate, and is recommended against by @vehtari2017practical.]. -->
<!-- Another approach is to take into account that areal data is typically produced by aggregating higher resolution data, so as to be a particular instance of the broader challenge of inference about a variable at a different resolution to that it was observed at, known in geostatistics as the change-of-support problem [@gelfand2001change] and dating to foundational work on block kriging [@krige1951statistical; @matheron1976forecasting]. -->
<!-- Ideas from change-of-support modelling are applied by @kelsall2002modeling to consider areal data as coming about by an aggregation of a continuously-indexed Gaussian process, resulting in a covariance structure between two areas given by the average covariance between two points chosen randomly from those areas. -->
<!-- This type of model is particularly natural in the log-Gaussian Cox process modelling framework [@li2012log; @diggle2013spatial; @taylor2015bayesian; @johnson2019spatially], `lgcp` [@taylor2015bayesian] and `SDALGCP` [@johnson2019spatially] packages. -->
<!-- Inference for aggregated data has recently been advanced by @wilson2018pointless who consider the SPDE approach of @lindgren2011explicit, using `R-INLA`, and an empirical Bayes approach, using `TMB` [@kristensen2015tmb], and made available as a part of the `disaggregation` package [@nandi2020disaggregation]. -->

@@

Areal is often aptly conceptualised as arising from aggregation of point data, such that $y_i = \int_{A_i} y(s) \text{d}s$.
Exceptions include policies determined at an administrative level, such as the minimum wage or disease control measures, which have a genuinely discrete spatial structure\footnote{For data of this sort, there is less clear justification for using spatial smoothing. Realistically, data relate to many covariates, some number of which are likely have discrete spatial structure and others of which continuous spatial structure, such that the result is often an intermediate. It may be possible to model this explicitly, though the result might look similar to what is achieved using e.g. BYM2.}.
If the areal data we observe are indeed an aggregation of point data, why not use the higher resolution point data in our models rather than areal data?
Explainations include that (a) the underlying point data are unobserved, (b) although point data are collected, they may not be accessible due to privacy constraints, administrative practicality or storage capacity, and (c) the point data are available, but we decide not to use them in the model.
In the final case (c), researchers may prefer to use area-level models because models for point data are typically more complex, require more data, including covariate data which may not exist, and have higher computational burden.
Choosing to model the underlying data generating mechanism as either areal or point is often a matter of pragmatism.

@@

The latter benefit is basis for the statistical task of small-area estimation, which aims to produce reliable local estimates where small sample sizes lead to noisy data [@pfeffermann2013new].
In a spatial setting, this is often in small geographic areas, though the phrase "small-area" is not restricted to geographic areas and may be interpreted more broadly to mean any area where data are insufficient to make accurate local parameter inferences.
In the context of multilevel regression and post-stratification [@gelman1997poststratification], small-areas are generated by the intersection of demographic variables like age, gender and race, alongside geographic variables.
Due to the cost of gathering samples, a survey may be designed to give reliable estimates at at an aggregated level but not at a small-area level.
Although direct estimators of local parameters are unbiased, when data are sparse the total error may be reduced by accepting some bias in exchange for reduced variance using so-called indirect estimators.
Smoothing approaches use information from similar units to "borrow strength" from one parameter to another, with determining precisely what is meant by "similar" a central challenge.
@wakefield2020small review design-based approaches and model-based approaches to spatial analysis of health-indicators, including both area and unit-level analysis.

@@

A striking feature of Equation~\ref{eq:besag} is that the precision of $\phi_i$ is proportional to its number of neighbours $n_{\delta i}$.
It follow that as $n_{\delta i} \to \infty$ then $\text{Var}(\phi_i) \to 0$.
This is illustrated by Figure \ref{fig:tikz2} where the area on the right is repeatedly divided such that its number of neighbours increases by one at each step.
This property is a consequence of averaging the conditional mean over a greater number of areas, which, in certain situations, can correspond to a greater amount of information.
However, if the amount of information in the shaded area remains fixed, it is inappropriate that $\text{Var}(\phi_1)$ should tend to zero just as a result of drawing additional, arbitrary, boundaries.
In the image analysis setting this modelling assumption is reasonable: each pixel represents a fixed amount of information and a higher pixel density represents a greater amount of information.
On the other hand, in public health and epidemiology, drawing boundaries to create additional regional areas cannot be expected to correspond to a greater amount of information and this assumption is not appropriate.

@@

<!-- ## Weighted ICAR \label{sec:icar} -->

<!-- The Besag model is a special case of a more general class of (zero-mean) ICAR models in which each neighbour may not be weighted equally. -->
<!-- These models can be specified in terms of scaled weights $\{b_{ij}\}_{j \sim i}$ and a precision vector $\kappa = (\kappa_1, \ldots, \kappa_n)^\top$ such that $\phi_i \, | \, \phi_{-i} \sim \N ( \sum_{j: j \sim i} b_{ij} \phi_j, (\kappa_i \tau_\phi)^{-1} )$. -->
<!-- The structure matrix $R$ corresponding to the above full conditionals is given by $R = D_\kappa(I - B)$, where $B$ has the entries $b_{ij}$ for $i \sim j$, diagonal entries $b_{ii} = 0$ and $b_{ij} = 0$ for $i \nsim j$ and the matrix $D_\kappa$ is given by $\text{diag}(\kappa_1, \ldots, \kappa_n)$. -->
<!-- As the structure matrix is symmetric we must have the condition $-b_{ij}\kappa_i = -b_{ji}\kappa_j$. -->
<!-- To meet this condition, it is often simpler to use an unscaled weights matrix $W = D_\kappa B$ such that $R = D_\kappa - W$. -->
<!-- For example, in the Besag model $W$ corresponds to the adjacency matrix. -->
<!-- The scaled weights can then be recovered by $b_{ij} = w_{ij} / \kappa_i$ where $\kappa_i = \sum_{k: k \sim i} w_{ik}$. -->
<!-- A thorough discussion of methods for specifying $W$ is provided by @duncan2017spatial. -->
<!-- Much of the work in this area focuses on the case where the geometry is a lattice. -->

@@

The simplest approach is to use a single point, especially one which is representative of the area, a natural choice being the centroid $c_i \in A_i$ given by the arithmetic mean of the latitude and longitude.
This results in the centroid kernel
\begin{equation}
    K(A_i, A_j) = k(c_i, c_j).
\end{equation}
<!-- More broadly, given a weighting distribution $W_i$ with probability density proportional to $w_i(s)$ over $A_i$, weighted centroids could be used in the above equation. -->
The centroid kernel has been used by @wakefield1999spatial in an environmental epidemiology setting and @best2005comparison in a model comparison study, both choosing the exponential kernel $k(s_i, s_j) = \exp \left( - |s_i - s_j| / l \right)$.
The former fix the length-scale $l$ using a semi-variogram and the later place a prior on the inverse length-scale.
In their simulation experiment, \citet[Section 3]{best2005comparison} used data representing heterogeneous exposure to air pollution, including elevated rates of exposure near two hypothetical point source locations, and found that the centroid kernel tended to over-smooth the high-risk areas, but it is not suprising that a stationary covariance structure would struggle to recover non-stationary spatial structure).
More recently, @teh2021efficient used a centroid kernel as a part of a spatio-temporal Gaussian process model to infer the reproduction number of COVID-19.

@@

\begin{figure}
\centering
\includegraphics[width=\textwidth]{depends/integration-method.pdf}
\caption{Three ways to choose integration points with $L_i = 10$ for all $i$ in Malawi, as implemented by \texttt{sf::st\_sample} [@pebesma2018sf].}
\label{fig:41}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics{depends/simulation-geometries.pdf}
\caption{Simulation geometries.}
\label{fig:51}
\end{figure}

@@

\begin{table}[]
\small
\begin{tabularx}{\textwidth}{@{}lX@{}}
\toprule
Simulation model & Additional details \\
 \midrule
\hypertarget{S1}{S1}. \textit{IID} & $\phi \sim \mathcal{N}(0, I_n)$ \\
\hypertarget{S2}{S2}. \textit{Besag} & $\phi \sim \mathcal{N}(0, (R^\star)^{-})$ as described in Section \ref{sec:besag} where $R^\star$ is the scaled structure matrix \\
\hypertarget{S3}{S3}. \textit{IK} & $\phi \sim \mathcal{N}(0, K^\star)$ as described in Section \ref{sec:ik} where $K_{ij}$ is calculated via Equation~\ref{eq:mcintegratedkernel} using the Mat\'{e}rn kernel with $\nu = 3/2$, $l = 2.5$ and $L_i = 100$ samples are drawn uniformly from each area.
Like the Besag model, we scaled the Gram matrix to have generalised variance one \\
\bottomrule
\end{tabularx}
\caption{The three simulation models from which we generate $\phi$.}
\label{tab:simulationmodels}
\small
\end{table}

@@

We fit eight inferential models, each of which differing in the spatial random effect specification (Table \ref{tab:inferentialmodels}).

\begin{table}
\small
\begin{tabularx}{\textwidth}{llX}
\toprule
Inferential model & Algorithm & Additional details \\
 \midrule
\hypertarget{I1}{I1}. \textit{Constant} & INLA &
No spatial random effects \label{row:I1} \\
\hypertarget{I2}{I2}. \textit{IID} & INLA &
$\phi \sim \mathcal{N}(0, \tau_\phi^{-1} I_n)$\\
\hypertarget{I3}{I3}. \textit{Besag} & INLA &
$\phi \sim \mathcal{N}(0, (\tau_\phi R^\star)^{-})$ following additional recommendations in~\ref{app:freni}  \\
\hypertarget{I4}{I4}. \textit{BYM2} & INLA &
$\phi = \tau_\phi^{-1} \left( \sqrt{1- \pi} \, v + \sqrt{\pi} \, u^\star \right)$ with a $\text{Beta}(0.5, 0.5)$ prior on $\pi \in [0, 1]$ \\
\hypertarget{I5}{I5}. \textit{FCK} & INLA &
$\phi \sim \mathcal{N}(0, \tau_\phi^{-1} K)$ with $K_{ij} = k(c_i, c_j)$ where the length-scale $l$ is fixed \\
\hypertarget{I6}{I6}. \textit{CK} & NUTS & As in model~\hypertarget{I5}{I5}, with length-scale prior $l \sim \mathrm{Inv{\text-}Gamma}(a, b)$ \\
\hypertarget{I7}{I7}. \textit{FIK} & INLA & $\phi \sim \mathcal{N}(0, \tau_\phi^{-1} K)$ with $K_{ij} = \frac{1}{10^2} \sum_{l = 1}^{10} \sum_{m = 1}^{10} k \left( s^{(i)}_l, s^{(j)}_m \right)$ \newline with hexagonal integration point spacing and fixed length-scale $l$ \\
\hypertarget{I8}{I8}. \textit{IK} & NUTS & As in model~\hypertarget{I7}{I7}, with length-scale prior $l \sim \mathrm{Inv{\text-}Gamma}(a, b)$ \\
\bottomrule
\end{tabularx}
\caption{Each inferential model is implemented as a part of the \textsf{R} package \texttt{bsae} available from \url{github.com/athowes/bsae}.}
\label{tab:inferentialmodels}
\small
\end{table}

@@

For the precision, we placed a half-Gaussian prior on the standard deviation [@gelman2006prior] such that $\sigma_\phi \sim \mathcal{N}_+(0, 2.5^2)$.
The weakly informative value 2.5 was chosen to avoid placing significant prior density on the region $\sigma_\phi > 5$, which after a logistic transformation facilitates variation on the probability scale very close to either zero or one, neither of which we assumed to be plausible.
A weakly informative $\mathcal{N}(-2, 1)$ prior was placed on $\beta_0$, setting most of the prior probability density for $\rho_i$ within a range $[0, 0.25]$ typical for a disease prevalence.

@@

Following @stein1999interpolation, for the areal kernel models we used the Matérn kernel $k: \Sc \times \Sc \to \mathbb{R}$ given by
\begin{equation}
k(s, s') =
\frac{1}{2^{\nu - 1}\Gamma(\nu)} \left(\frac{\sqrt{2\nu}\lvert s - s' \rvert}{l}\right)^\nu
B_\nu\left(\frac{\sqrt{2\nu}\lvert s - s' \rvert}{l}\right), \label{eq:matern}
\end{equation}
where $B_\nu$ is the modified Bessel function of the second kind, $|s - s'|$ is the Euclidean distance between $s$ and $s'$, $\nu$ is the smoothness hyperparameter and $l$ is the length-scale hyperparameter on the latitude-longitude scale.
We fixed the smoothness parameter, which is otherwise typically unidentifiable from data, to be $3/2$, matching that used in simulation model \hyperlink{S3}{S3}, and convenient in that it simplifies Equation \ref{eq:matern} to be
\begin{equation}
k(s, s') = \left(1 + \sqrt{3} \lvert s - s' \rvert / l \right) \exp \left(- \sqrt{3} \lvert s - s' \rvert / l \right).
\end{equation}
Taking a similar approach to @best1999bayesian, in models \hyperlink{I5}{I5} and \hyperlink{I7}{I7} we fixed the length-scale such that points an average distance apart in the model have 1\% correlation  a priori, independent of the data.
In models \hyperlink{I6}{I6} and \hyperlink{I8}{I8}, we used a length-scale prior $l \sim \mathrm{Inv{\text-}Gamma}(a, b)$, with parameters $a$ and $b$ chosen for each model such that 1\% of the prior mass is below 0.1 and 1\% of the prior mass is above the maximum distance between points in the model [@betancourt2017robust].
For the integration points we set $L_i = 10$ using a hexagonal spacing structure, as with the central panel of Figure \ref{fig:51}.
The true number of integration points may be 1-2 above or below 10, as `sf::st_sample` with `type = "hexagonal"` is not guaranteed to be exact.
We are limited to this relatively small number by the computational costs of Model \hyperlink{I8}{I8}.
For Model \hyperlink{I6}{I6} although it is feasible to use a much larger number of integration points, since the Gram matrix is only computed once, we chose not to for comparability.

@@

To assess the coverage of our estimates, we considered probability integral transform (PIT) histograms and empirical cumulative distribution function (ECDF) difference plots [@sailynoja2021graphical].
We estimated the quantile $q_i = F(\omega_i)$ of the true value within the marginal posterior using numerical integration.
For calibrated models, over repeated simulations, $q_i \sim \mathcal{U}[0, 1]$ such that for any given nominal significance level $1 - \alpha$, the proportion of quantile-based credible intervals containing the true value $\omega_i$, should be $1 - \alpha$.

@@

```{r results="asis"}
#' Some of the lines should not be included
lines_remove <- c(1)
cat(readLines("depends/metric-table.txt")[-lines_remove], sep = "\n")
```

>>>>

---
title: Understanding models for spatial structure in small-area estimation
author:
  - name: Adam Howes
    email: ath19@ic.ac.uk
    affiliation: A
    corresponding: ath19@ic.ac.uk
  - name: Harrison Zhu
    affiliation: A
  - name: Yidan Xu
    affiliation: C
  - name: Samir Bhatt
    affiliation: D
  - name: Jeffrey W. Eaton
    affiliation: B
  - name: Seth R. Flaxman
    affiliation: E
address:
  - code: A
    address: Department of Mathematics, Imperial College London
  - code: B
    address: MRC Centre for Global Infectious Disease Analysis, Imperial College London
  - code: C
    address: Department of Statistics, University of Michigan
  - code: D
    address: Department of Public Health, University of Copenhagen
  - code: E
    address: Department of Computer Science, University of Oxford
abstract: |
  |  **Background:** Spatial correlation between small-areas is typically accounted for within a generalised linear mixed model setting using spatial random effects. However, commonly used models for spatial random effects based upon adjacency relations, like the Besag model, make unrealistic and unsatisfying spatial assumptions, which seem particularly dubious for irregular geometries. Furthermore, they do not take into account that across many settings areal data is generated by aggregating continuous point data. Defining spatial random effects which instead correspond to aggregated Gaussian processes gives a more intuitively convincing correlation structure, and allows tools from kernel methods to be used in models for areal data.
  |
  |  **Methods:** In a comprehensive simulation study, we used a proper scoring rule to evaluate the performance of different spatial random effect specifications. We performed these simulations under model misspecification and across a range of vignette and realistic geometries with different regularities. We also compared model performance in estimating district-level HIV prevalence from PHIA household survey data across four countries in sub-Saharan Africa, using cross-validation and spatial cross-validation.
  |
  |  **Results:**
  |
  |  **Conclusions:**

@@

Spatial random effects are frequently used to model spatial variation in areal data [@haining2003spatial; @cramb2018investigation].
Gaussian Markov random fields (GMRFs) [@rue2005gaussian], which combine a Gaussian distribution with Markov conditional independence assumptions between areas, are the most common class of models used to specify spatial random effects.
Using a GMRF typically reflects the assumption that observations made in areas close together are correlated, and more distant relationships may be ignored.
The simplest GMRF model is arguably that of @besag1991bayesian, where information is borrowed equally from each adjacent area.
This model requires minimal additional modelling choices and is widely implemented, including as a part of the `R-INLA` package [@rue2017bayesian], popular within spatial statistics.
Use of this model is widespread, including in agriculture [@oliver2015soil], ecology [@saracco2010modeling], epidemiology [@lawson2013statistical], image analysis [@schmid2006bayesian], neuroscience [@gossl2001bayesian] and public health [@dwyer2015drinking].
However, for irregular geometries like the administrative divisions of a country, the assumptions made by the Besag model about space are unrealistic.
We hypothesised that incorporating a spatial structure more faithfully to the specific geometry would improve the performance of small-area estimation models.
Here, we set out to test this hypothesis, and in doing so provide practical recommendations and further understanding of models for spatial structure.
<!-- @gutreuter2019improving use the SAR model, which is still adjacency based but is not exactly the Besag model--restructure introduction to be more general and include introduction of other adjacency based models (which all have the same criticisms)? -->

@@

Within the GRMF framework, attempts to more accurately reflect irregular spatial structure have defined weights specifying the extent to which neighbours are related.
@duncan2017spatial compared seventeen methods for specifying these weights, but surprisingly did not find any which outperform the Besag model, though this conclusion was specific to the (often-analysed) Scottish lip cancer example, and based on the recommended against [@vehtari2017practical] deviance information criteria (DIC).
Another approach is to take into account that areal data is typically produced by aggregating higher resolution data, so as to be a particular instance of the broader challenge of inference about a variable at a different resolution to that it was observed at, known in geostatistics as the change-of-support problem [@gelfand2001change] and dating to foundational work on block kriging [@krige1951statistical; @matheron1976forecasting].
Ideas from change-of-support modelling are applied by @kelsall2002modeling to consider areal data as coming about by an aggregation of a continuously-indexed Gaussian process, resulting in a covariance structure between two areas given by the average covariance between two points chosen randomly from those areas.
This type of model is particularly natural in the log-Gaussian Cox process modelling framework [@li2012log; @diggle2013spatial; @taylor2015bayesian; @johnson2019spatially], `lgcp` [@taylor2015bayesian] and `SDALGCP` [@johnson2019spatially] packages.
Inference for aggregated data has recently been advanced by @wilson2018pointless who consider the SPDE approach of @lindgren2011explicit, using `R-INLA`, and an empirical Bayes approach, using `TMB` [@kristensen2015tmb], and made available as a part of the `disaggregation` package [@nandi2020disaggregation].

@@

Areal data is often aptly conceptualised as arising from aggregation of point data, such that $y_i = \int_{A_i} y(s) \text{d}s$.
Exceptions include policies determined at an administrative level, such as the minimum wage or disease control measures, which have a genuinely discrete spatial structure.
<!-- Note that, for data of this sort, there is less clear justification for using spatial smoothing. -->
<!-- Realistically, data relate to many covariates, some number of which are likely have discrete spatial structure and others of which continuous spatial structure, such that the result is often an intermediate. -->
<!-- It may be possible to model this explicitly, though the result might look similar to what is achieved using e.g. BYM2. -->
If the areal data we observe are indeed an aggregation of point data, why not use the higher resolution point data in our models rather than areal data?
Explanations include that (a) the underlying point data are unobserved, (b) although point data are collected, they may not be accessible due to privacy constraints, administrative practicality or storage capacity, and (c) the point data are available, but we decide not to use them in the model.
In the final case (c), researchers may prefer to use area-level models as models for point data are typically more complex, require more data, are less immediately applicable to area-level policy making, and have higher computational burden.
Furthermore, seemly point data may actual be areal, such as data observed at polling stations or health facilities which individuals from the surrounding area travel to.
As such, choosing to model the underlying data generating mechanism as either areal or point is often a matter of pragmatism.

@@

The latter benefit is basis for the statistical task of small-area estimation, which aims to produce reliable local estimates where small sample sizes lead to noisy data [@pfeffermann2013new].
In a spatial setting, this is often in small geographic areas, though the phrase "small-area" is not restricted to geographic areas and may be interpreted more broadly to mean any area where data are insufficient to make accurate local parameter inferences.
In the context of multilevel regression and post-stratification [@gelman1997poststratification], small-areas are generated by the intersection of demographic variables like age, gender and race, alongside geographic variables.
Due to the cost of gathering samples, a survey may be designed to give reliable estimates at at an aggregated level but not at a small-area level.
Although direct estimators of local parameters are unbiased, when data are sparse the total error may be reduced by accepting some bias in exchange for reduced variance using so-called indirect estimators.
Smoothing approaches use information from similar units to "borrow strength" from one parameter to another, with determining precisely what is meant by "similar" a central challenge.
For a recent review of both design-based and model-based approaches to spatial analysis of health-indicators, including both area and unit-level analysis, see @wakefield2020small.

@@

A striking feature of Equation \ref{eq:besag} is that the precision of $\phi_i$ is proportional to its number of neighbours $n_{\delta i}$.
It follow that as $n_{\delta i} \to \infty$ then $\text{Var}(\phi_i) \to 0$.
This is illustrated by Figure \ref{fig:tikz2} where the area on the right is repeatedly divided such that its number of neighbours increases by one at each step.
This property is a consequence of averaging the conditional mean over a greater number of areas, which, in certain situations, can correspond to a greater amount of information.
However, if the amount of information in the shaded area remains fixed, it is inappropriate that $\text{Var}(\phi_1)$ should tend to zero just as a result of drawing additional, arbitrary, boundaries.
In the image analysis setting this modelling assumption is reasonable: each pixel represents a fixed amount of information and a higher pixel density represents a greater amount of information.
On the other hand, in public health and epidemiology, drawing boundaries to create additional regional areas cannot be expected to correspond to a greater amount of information and this assumption is not appropriate.

@@

## Weighted ICAR \label{sec:icar}

The Besag model is a special case of a more general class of (zero-mean) ICAR models in which each neighbour may not be weighted equally.
These models can be specified in terms of scaled weights $\{b_{ij}\}_{j \sim i}$ and a precision vector $\kappa = (\kappa_1, \ldots, \kappa_n)^\top$ such that $\phi_i \, | \, \phi_{-i} \sim \N ( \sum_{j: j \sim i} b_{ij} \phi_j, (\kappa_i \tau_\phi)^{-1} )$.
The structure matrix $R$ corresponding to the above full conditionals is given by $R = D_\kappa(I - B)$, where $B$ has the entries $b_{ij}$ for $i \sim j$, diagonal entries $b_{ii} = 0$ and $b_{ij} = 0$ for $i \nsim j$ and the matrix $D_\kappa$ is given by $\text{diag}(\kappa_1, \ldots, \kappa_n)$.
As the structure matrix is symmetric we must have the condition $-b_{ij}\kappa_i = -b_{ji}\kappa_j$.
To meet this condition, it is often simpler to use an unscaled weights matrix $W = D_\kappa B$ such that $R = D_\kappa - W$.
For example, in the Besag model $W$ corresponds to the adjacency matrix.
The scaled weights can then be recovered by $b_{ij} = w_{ij} / \kappa_i$ where $\kappa_i = \sum_{k: k \sim i} w_{ik}$.
A thorough discussion of methods for specifying $W$ is provided by @duncan2017spatial.
Much of the work in this area focuses on the case where the geometry is a lattice.

@@

The simplest approach is to use a single point, especially one which is representative of the area, a natural choice being the centroid $c_i \in A_i$ given by the arithmetic mean of the latitude and longitude.
This results in the centroid kernel
\begin{equation}
    K(A_i, A_j) = k(c_i, c_j).
\end{equation}
<!-- More broadly, given a weighting distribution $W_i$ with probability density proportional to $w_i(s)$ over $A_i$, weighted centroids could be used in the above equation. -->
The centroid kernel has been used by @wakefield1999spatial in an environmental epidemiology setting and @best2005comparison in a model comparison study, both choosing the exponential kernel $k(s_i, s_j) = \exp \left( - |s_i - s_j| / l \right)$; as well as more recently by @teh2021efficient as a part of a spatio-temporal Gaussian process model to infer the reproduction number of COVID-19.
@wakefield1999spatial fix the length-scale $l$ using a semi-variogram and @best2005comparison place a prior on the inverse length-scale.
\citet[Section 3]{best2005comparison} simulated data representing heterogeneous exposure to air pollution, including elevated rates of exposure near two hypothetical point source locations, and found that the centroid kernel tended to over-smooth the high-risk areas, though it is unsuprising that a stationary covariance would struggle to recover non-stationary structure.

@@

\begin{figure}
\centering
\includegraphics[width=\textwidth]{depends/integration-method.pdf}
\caption{Three ways to choose integration points with $L_i = 10$ for all $i$ in Malawi, as implemented by \texttt{sf::st\_sample}.}
\label{fig:41}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics{depends/simulation-geometries.pdf}
\caption{The seven simulation geometries that we considered.}
\label{fig:51}
\end{figure}

@@

\begin{table}[]
\small
\begin{tabularx}{\textwidth}{@{}lX@{}}
\toprule
Simulation model & Additional details \\
 \midrule
\hypertarget{S1}{S1}. \textit{IID} & $\phi \sim \mathcal{N}(0, I_n)$ \\
\hypertarget{S2}{S2}. \textit{Besag} & $\phi \sim \mathcal{N}(0, (R^\star)^{-})$ as described in Section \ref{sec:besag} where $R^\star$ is the scaled structure matrix \\
\hypertarget{S3}{S3}. \textit{IK} & $\phi \sim \mathcal{N}(0, K^\star)$ as described in Section \ref{sec:ik} where $K_{ij}$ is calculated via Equation \ref{eq:mcintegratedkernel} using the Mat\'{e}rn kernel with $\nu = 3/2$, $l = 2.5$ and $L_i = 100$ samples are drawn uniformly from each area.
Like the Besag model, we scaled the Gram matrix to have generalised variance one \\
\bottomrule
\end{tabularx}
\caption{The three simulation models from which we generate $\phi$.}
\label{tab:simulationmodels}
\small
\end{table}

@@

We fit eight inferential models, each of which differing in its spatial random effect specification (Table \ref{tab:inferentialmodels}).

\begin{table}
\small
\begin{tabularx}{\textwidth}{llX}
\toprule
Inferential model & Algorithm & Additional details \\
 \midrule
\hypertarget{I1}{I1}. \textit{Constant} & INLA &
No spatial random effects \label{row:I1} \\
\hypertarget{I2}{I2}. \textit{IID} & INLA &
$\phi \sim \mathcal{N}(0, \tau_\phi^{-1} I_n)$\\
\hypertarget{I3}{I3}. \textit{Besag} & INLA &
$\phi \sim \mathcal{N}(0, (\tau_\phi R^\star)^{-})$ following additional recommendations in \ref{app:freni}  \\
\hypertarget{I4}{I4}. \textit{BYM2} & INLA &
$\phi = \tau_\phi^{-1} \left( \sqrt{1- \pi} \, v + \sqrt{\pi} \, u^\star \right)$ with a $\text{Beta}(0.5, 0.5)$ prior on $\pi \in [0, 1]$ \\
\hypertarget{I5}{I5}. \textit{FCK} & INLA &
$\phi \sim \mathcal{N}(0, \tau_\phi^{-1} K)$ with $K_{ij} = k(c_i, c_j)$ where the length-scale $l$ is fixed \\
\hypertarget{I6}{I6}. \textit{CK} & NUTS & As in model \hypertarget{I5}{I5}, with length-scale prior $l \sim \mathrm{Inv{\text-}Gamma}(a, b)$ \\
\hypertarget{I7}{I7}. \textit{FIK} & INLA & $\phi \sim \mathcal{N}(0, \tau_\phi^{-1} K)$ with $K_{ij} = \frac{1}{10^2} \sum_{l = 1}^{10} \sum_{m = 1}^{10} k \left( s^{(i)}_l, s^{(j)}_m \right)$ \newline with hexagonal integration point spacing and fixed length-scale $l$ \\
\hypertarget{I8}{I8}. \textit{IK} & NUTS & As in model \hypertarget{I7}{I7}, with length-scale prior $l \sim \mathrm{Inv{\text-}Gamma}(a, b)$ \\
\bottomrule
\end{tabularx}
\caption{Each inferential model is implemented as a part of the \textsf{R} package \texttt{bsae} available from \url{github.com/athowes/bsae}.}
\label{tab:inferentialmodels}
\small
\end{table}

@@

We placed a half-Gaussian prior on the standard deviation [@gelman2006prior] such that $\sigma_\phi \sim \mathcal{N}_+(0, 2.5^2)$.
The weakly informative value 2.5 was chosen to avoid placing significant prior density on the region $\sigma_\phi > 5$, which after a logistic transformation facilitates variation on the probability scale very close to either zero or one, neither of which we assumed to be plausible.
A weakly informative $\mathcal{N}(-2, 1)$ prior was placed on $\beta_0$, setting most of the prior probability density for $\rho_i$ within a range $[0, 0.25]$ typical for a disease prevalence.

@@

Following @stein1999interpolation, for the areal kernel models we used the Matérn kernel $k: \Sc \times \Sc \to \mathbb{R}$ given by
\begin{equation}
k(s, s') =
\frac{1}{2^{\nu - 1}\Gamma(\nu)} \left(\frac{\sqrt{2\nu}\lvert s - s' \rvert}{l}\right)^\nu
B_\nu\left(\frac{\sqrt{2\nu}\lvert s - s' \rvert}{l}\right), \label{eq:matern}
\end{equation}
where $B_\nu$ is the modified Bessel function of the second kind, $|s - s'|$ is the Euclidean distance between $s$ and $s'$, $\nu$ is the smoothness hyperparameter and $l$ is the length-scale hyperparameter on the latitude-longitude scale.
We fixed the smoothness parameter, which is otherwise typically unidentifiable from data, to be $3/2$, matching that used in simulation model \hyperlink{S3}{S3}, and convenient in that it simplifies Equation \ref{eq:matern} to be
\begin{equation}
k(s, s') = \left(1 + \sqrt{3} \lvert s - s' \rvert / l \right) \exp \left(- \sqrt{3} \lvert s - s' \rvert / l \right).
\end{equation}
Taking a similar approach to @best1999bayesian, in models \hyperlink{I5}{I5} and \hyperlink{I7}{I7} we fixed the length-scale such that points an average distance apart in the model have 1\% correlation  a priori, independent of the data.
In models \hyperlink{I6}{I6} and \hyperlink{I8}{I8}, we used a length-scale prior $l \sim \mathrm{Inv{\text-}Gamma}(a, b)$, with parameters $a$ and $b$ chosen for each model such that 1\% of the prior mass is below 0.1 and 1\% of the prior mass is above the maximum distance between points in the model [@betancourt2017robust].
For the integration points we set $L_i = 10$ using a hexagonal spacing structure, as with the central panel of Figure \ref{fig:51} -- though `sf::st_sample` with `type = "hexagonal"` does not guarantee exactly the specified number of samples are returned [@pebesma2018sf].
We are limited to this relatively small number by the computational costs of Model \hyperlink{I8}{I8}.
For Model \hyperlink{I6}{I6} although it is feasible to use a much larger number of integration points, since the Gram matrix is only computed once, we chose not to for comparability.

@@

To assess the coverage of our estimates, we considered probability integral transform (PIT) histograms [@dawid1984present] and empirical cumulative distribution function (ECDF) difference plots [@aldor2013power; @sailynoja2021graphical].
We estimated the quantile $q_i = F(\omega_i)$ of the true value within the marginal posterior using numerical integration.
For calibrated models, over repeated simulations, $q_i \sim \mathcal{U}[0, 1]$ such that for any given nominal coverage $1 - \alpha$, the proportion of quantile-based credible intervals containing the true value $\omega_i$, in other words the empirical coverage, should also be $1 - \alpha$.

@@

```{r results="asis"}
#' Some of the lines should not be included
lines_remove <- c(1)
